Investigation of ant cuticle dataset using image texture analysis

### 2022-09-21 paper/main.tex
Proof (#22)
* proof version

* fix paragraph

\FloatBarrier Some classified results from the K-views are shown in Figure
\ref{fig:kviews_segmented}. A training set of 550 patches for background, 455
patches for rough, and 493 patches for smooth are used with patch sizes of 15
$\times$ 15 and 19 $\times$ 19. Hence, the three classes are utilized in the
clustering. These patches are extracted from two rough and two smooth images
with sizes of 608 $\times$ 608. The K-views algorithm converges early although
we set the maximum number of iterations to be 1000. In order to classify an
image with K-views, the input image is split into patches. Then, each patch is
assigned to a cluster based on the distance to the cluster. If there are more
`smooth' patches, than `rough' patches, then the image will be classified as
rough. These experimental results are preliminary due to the minimal number of
source images used and future work will explore a more expansive approach to the
problem.

>>>>

\FloatBarrier Some classified results from the K-views are shown in Figure
\ref{fig:kviews_segmented}. A training set of 550 patches for background, 455
patches for rough, and 493 patches for smooth are used with patch sizes of 15
$\times$ 15 and 19 $\times$ 19. These patches are extracted from two rough and
two smooth images with sizes of 608 $\times$ 608. The K-views algorithm
converges early although we set the maximum number of iterations to be 1000.
These experimental results are preliminary due to the minimal number of source
images used and future work will explore a more expansive approach to the
problem.
